%& -job-name=Matthew_Santos_CV
% Matthew Santos
% Generic CV
% Last Updated Nov 2024
% (Compile with pdfLatex)
%------------------------

\documentclass{../templates/resume}
\usepackage[backend=bibtex,style=ieee,sorting=ynt]{biblatex}
\addbibresource{../bibliography/publications.bib}
\begin{document}
	\header
	%\vfill
	
	% Metadata (Job Specific Keywords)
	\hypersetup{
		pdftitle={Matthew Santos CV},
		pdfsubject={CV},
		pdfkeywords={Electrical Engineer}
	}
	
	\section{EDUCATION}
		%\resumeEntry{University of Windsor}{Windsor, ON}{Faculty of Engineering}{Expected 2025}{Candidate for Masters of Applied Science, Electrical Engineering}{}
		\resumeEntry{University of Windsor}{Windsor, ON}{Faculty of Engineering}{2018}{Bachelor of Applied Science, Electrical Engineering, Specialization in Electronics}{}
		\resumeEntry{University of Waterloo}{Waterloo, ON}{Faculty of Science}{2015}{Bachelor of Science, Physics Minor}{}
	\section{PROFESSIONAL EXPERIENCE}
		\resumeEntry{University of Windsor}{Windsor, ON}{Research Assistant}{Jan. 2022 - Sept. 2022}{Developed embeded systems to acquire and calibrate arrays of experiemental analog sensors.}{}
		\resumeEntry{Helpwear Inc}{Toronto, ON}{Mitacs Accelerate Intern}{Sept. 2018 - Jan. 2019}{Researched a method to reduce floating ground effect on wearable electrocardiography sensors.}{}
		\resumeEntry{Alcohol Countermeasures Systems}{Toronto, ON}{Junior Metrology Lab Researcher}{Sept. 2012 - Apr. 2013}{Led research and development initiatives in the area of electrochemical and optical sensors.}{}
		\resumeEntry{Methes Energies International}{Mississauga, ON}{Assistant Chemist}{Sept. 2011 - Apr. 2012}{Implemented ASTM testing procedures and developed innovative measurement methodologies.}{}
		\resumeEntry{National Research Council Canada}{Victoria,BC}{Co-op Student}{Jan. 2011 - Apr. 2011}{Developed and implemented the data processing pipeline for the Next Generation Virgo Cluster Survey.}{}
	\section{SELECT PROJECTS}
		\resumeEntry{MonoPulse}{University of Windsor}{Electrical and Computer Engineering Department}{July 2019 - Apr. 2025}{A novel single wire ECG acquisition system utilizing advanced filtering techniques.}{}
		\resumeEntry{GroGuardian}{University of Windsor}{Electrical Micro \& Nano Devices and Sensor Research Centre}{Jan. 2022 - Sept. 2022}{Apparatus for precise measurement and calibration of experimental electrochemical sensor arrays.}{}
		\resumeEntry{GroGenesis}{University of Windsor}{Electrical Micro \& Nano Devices and Sensor Research Centre}{Jan. 2022 - Sept. 2022}{Embedded system for remote monitoring and analysis of various atmospheric properties.}{}
		\resumeEntry{Capstone Project}{University of Windsor}{Electrical and Computer Engineering Department}{Jan 2017 - Dec. 2017}{Cardless security system featuring biometric identification through electrocardiogram signals.}{}
		%\resumeEntry{Electronics I Design Project}{University of Windsor}{Electrical and Computer Engineering Department}{Jan 2016 - Apr. 2016}{Three phase open loop configuration PWN generator for use in low speed brushless motor control.}{}
	\section{CERTIFICATIONS}
		\resumeSkillEntry{St. John Ambulance}{Standard First Aid CPR A + AED}{Nov. 2024 - Nov 2027}
		\resumeSkillEntry{Cadence}{Analog Mixed-Signal Design Methodology and FinFET Layout Training using GF12LP PDK}{2022}
		\resumeSkillEntry{Cadence}{Analog Mixed Signal Design Methodology - Train the Trainer using GPDK045 PDK}{2020}
		\resumeSkillEntry{University of Windsor}{Technical Writing Series - Continuing Education Department}{2019}
	\section{PUBLICATIONS}
		\nocite{*}
		\printbibliography[heading=none]
	\section{SCHOLARSHIPS \& AWARDS}
		\resumeSkillEntry{GA/TA Award Nomination}{University of Windsor}{May 2019}
		\resumeSkillEntry{Fredrick Atkins Graduate Scholarship}{University of Windsor}{May 2019,2020}
		\resumeSkillEntry{Best Capstone Project}{University of Windsor Electrical Engineering Department}{Aug. 2018}
		\resumeSkillEntry{Merit Scholarship}{University of Waterloo Electrical Engineering Department}{Sept. 2009}
		\resumeSkillEntry{Engineering Inspiration Award}{First Robotics Waterloo Regional}{Mar. 2009}
		%\resumeSkillEntry{RJ Mcarthy}{Halton Catholic District School Board}{June 2009}
	\vfill
	\pagebreak
	\section{SUPERVISION, MENTORSHIP, \& TEACHING}
		%\resumeSkillEntry{Sole Invigilator}{University of Windsor}{Sept. 2019}
		\resumeEntry{Graduate Assistant}{University of Windsor}{Electrical and Computer Engineering Department}{Sept. 2018 - Apr. 2019}{}{
			\item GENG 2340 Electrical and Computing Fundamentals - Fall 2019
			\item ELEC 4000B Capstone Design Project - Spring 2019
			\item ELEC 4000A Capstone Design Project - Winter 2019
			\item GENG 2340 Electrical and Computing Fundamentals - Fall 2018
			}
		\resumeEntry{Mentor}{University of Windsor}{Electrical Micro \& Nano Devices and Sensor Research Centre}{Sept. 2018 - Apr. 2019}{}{
			\item Three outstanding scholars with literature reviews, embedded design, and FEM modeling.
			}
		\resumeEntry{Workshops Attended}{University of Windsor}{Centre for Teaching \& Learning}{Sept. 2018 - Apr. 2019}{}{
			\item Teaching and Learning Conference Volunteer Training - April 2019
			\item Creating a Teaching Dossier - April 2019
			\item Leading Effective Labs and Tutorials - Sept. 2018
			\item Grading and Providing Effective Feedback - Sept. 2018
			\item Designing Lessons and Creating Lesson Plans - Sept. 2018
			}
	\section{ACTIVITIES \& AFFILIATIONS}
		\resumeSkillEntry{IEEE Member}{Toronto Section}{Sept. 2018 - Present}
		\resumeSkillEntry{Alumni Representative}{University of Windsor Engineering Student Fund}{November 2018 - Sept. 2021}
		\resumeSkillEntry{Volunteer}{Lancer Leadership Conference}{Apr. 2019}
		\resumeSkillEntry{Volunteer}{Teaching and Learning Conference}{Feb. 2019}
		\resumeSkillEntry{First Robotics Mentor}{Teams 1334 \& 3161}{May 2007 - Sept. 2012}
	\section{SKILLS}
		\resumeSkillEntry{Computer Aided Design}{OrCAD, Allegro, Proteus, KiCAD, PSpice, Virtuoso, AutoCAD, MPLAB-X}{}
		\resumeSkillEntry{Electronics Implementation}{SPI, I2C, I2S, UART, Wifi, Bluetooth, PIC8/16/32, ATMEGA32, ESP32, Arduino, Reaspberry Pi}{}
		\resumeSkillEntry{Analytical Software}{COMSOL, ANSYS, Keysight EMPro, MATLAB, Igor Pro, LabView, SciDavis}{}
		\resumeSkillEntry{Instrumentation \& Control}{Signal Analysis, LNA, Advanced Filtering, Spectroscopy, Analytical Chemistry, Optical Imaging}{}
		\resumeSkillEntry{Computer Proficiencies}{C++, Python, Fortran, Assembly, Verlog, VHDL, HTML/CSS, Bash, PowerShell, Linux}{}
		\resumeSkillEntry{Other Skills}{Project Management, LaTeX, Research, Prototyping, Circuit Debugging, Soldering, Computational Science}{}
\end{document}

