%& -job-name=Matthew_Santos_Resume
% Matthew Santos
% Generic Resume
% Last Updated July 2025
% (Compile with pdfLatex)
%------------------------

\documentclass{../templates/resume}
\begin{document}
	\header\vfill
	
	% Metadata (Job Specific Keywords, limit it to 20 maximum)
	\hypersetup{
		pdftitle={Matthew Santos Resume},
		pdfsubject={Resume},
		pdfkeywords={Electrical Engineer, ASIC, Computer Aided Design, Research, Sensors, Physics, Programming, Prototyping, Mentoring, Signal Processing}
		% Additional Keywords
		% Electrical Engineer, ASIC, Computer Aided Design, Electronic Design, OrCAD, Allegro, Altium, Quartus, Proteus, Keysight EDA, Autodesk Fusion, KiCAD, MicroCap, Electronics Simulation, PSpice, ngSpice, MicroCap, TINA, Icarus, LTSpice, Integrated Circuit Design, Virtuoso, Spectre, Innovus, MAGIC, Mechanical Modeling, AutoCAD, Solidworks, FreeCAD, Programing, IDE, MPLAB-X, Keil Studio, STM32, Ardrino, Electronics Implementation, Communication, Protocals, SPI, I2C, I2S, UART, USB, TCP/IP, RS-232, RS-485, PS/2Antenna Systems Wifi, Bluetooth, RF 315/433MHz, WaveguidesMicrocontrollers PIC8/16/32, DSP32, ATMEGA32, ATtiny85, ARM-Cortex-M3System on Chip ESP32, STM32, Arduino, Raspberry Pi, Application Specific Integrated Circuits, ADuCM356, MAX30131, ADPD7008, AD9102, Robotics Servos, Steppers, Controllers, Encoders, IR Sensors, Analytical Software, Finite Element Analysis, COMSOL, ANSYS, Keysight Pathwave/EMPro, Elmer FEM, Numeric Computing Enviroments, MATLAB, Octave, Igor Pro, SciDavis, MAPLE, Labview, Data Visualization SciDavis, Igor Pro, ParaView, LabPlot, SuperMongo, Instrumentation, Control, Static Measurement, Digital Multimeter, LCR Meter, Source Measurement Unit, ESD Tester, Signal Analysis Osciliscope, Spectrum Analyzer, Vector Network Analyzer, Time-Domain Reflectometer,NI-PXI SystemSignal Generation Arbitrary Waveform Generator, Pulse Generator, AC/DC Power Supplies, Signal Preprocessing, LNA, LIA, FIR/IIR, Filters, PLL, Spectroscopy, Mass, Xray, MNR, IR, Gas ChromotographyGeneral Chemistry Titration, Analytical Balance, Ultrasonic Cleaner, Centrifuges, CalorimetersOptical Imaging Probe Station, Scanning Electron Microscope, Mass Flow Monitoring, Control, Computer Proficiencies, Programing Languages, C++, Python, Fortran, Assembly, Verlog, VHDL, HTML/CSS, Machine Learning SVM,KNN, Linux, Red Hat, CentOS, Debian, Automation, Scripting, Bash, PowerShell, VBScripts, MATLAB,Project Management, Planning, Budgeting, Negotiation, Scheduling, Documentation, LaTeX, Microsoft Office Suite, Research, Report Writing, Conference Papers, Abstracts, Presentations, Prototyping, 3D Printing, General Machining, Electronics Assembly, Circuit Debugging, Methodical Fault Finding, Divide and Conquer, Soldering, Traditional, Hot Air, Reflow, Computational Science,  Physics, Mathematical Modeling, Optimization, Pure Science, Technology, Sensors, Teamwork
	}
	
	\section{CERTIFICATIONS \& TECHNICAL SKILLS} %Reorder/Edit/Comment to be Job Specific
	% Certifications
	%\resumeSkillEntry{Professional Engineers Ontario}{National Professional Practise Exam}{TBD}
	\resumeSkillEntry{St. Johns Ambulance}{Standard First Aid CPR A + AED}{2024}
	\resumeSkillEntry{Cadence}{Analog Mixed-Signal Design Methodology and FinFET Layout Training using GF12LP PDK}{2022}
	\resumeSkillEntry{Cadence}{Analog Mixed Signal Design Methodology - Train the Trainer using GPDK045 PDK}{2020}
	\resumeSkillEntry{University of Windsor}{Technical Writing Series - Continuing Education}{2019}
	% Technical Skills
	\vspace{4pt}
	%\resumeSkillEntry{Semiconductor Process Nodes}{65nm, 12nm (Global Foundaries)}{} %commented out because certifications already cover this
	\resumeSkillEntry{Electronic}{Design (ASIC, AMS, PCB), Layout (up to 5 GHz), Simulation (PSpice, LTSpice, FEA), Verification, PCB Assembly}{}
	\resumeSkillEntry{CAD Software}{Cadence (OrCAD, Allegro, Virtuoso), Pathwave (ADS, EM Design), Quartus, AutoCAD, MPLAB Toolchain, KiCad}{} %Pathwave was formally Keysight (ADS, EMPro)
	\resumeSkillEntry{Programming}{MATLAB, C/C++, Python, VHDL/Verilog, LabView, HTML5/CSS3, Fortran, Shell Scripting, Git, LaTeX, Ubuntu}{}
	\resumeSkillEntry{Electronic Analysis}{Signal Integrity (VNA, LCR, TDR, LIA), ESD/EMC, Probe Stations, Environmental Chambers (Stress Testing)}{}
	\resumeSkillEntry{Materials Analysis}{Spectroscopy (Mass, X-ray, MNR), SEM Imaging, Gas Chromology, Atomic Force Microscopy, Titration}{}
	\resumeSkillEntry{Extended Proficiencies}{Signal Processing, Sensor Development, Interfaces (I2C, SPI, UART, USB, Wifi/BT, 433 MHz ISM)}{}
	\section{EDUCATION}
	\resumeEntry{University of Windsor}{Windsor, ON}{Faculty of Engineering}{2018}{Bachelor of Applied Science, Electrical Engineering, Specialization in Electronics}{}
	\resumeEntry{University of Waterloo}{Waterloo, ON}{Faculty of Science}{2015}{Bachelor of Science, Physics Minor}{}
	\section{WORK EXPERIENCE}
	%\resumeEntry{Company}{Location}{JobTitle}{Date}{subheading}{\item Compelling verb + job duty + key skills used = tangible result}
	\resumeEntry{Electrical Micro \& Nano Devices and Sensors Research Centre}{Windsor, ON}{Research Assistant}{Jan. 2022 - Sept. 2022}{}{
		\item Developed precision measurement apparatus for automated transducer characterization of novel sensor technologies
		\item Supervised and supported junior engineers and researchers in ongoing R\&D activities in applied sensor development
	}
	\resumeEntry{Helpwear}{Toronto, ON}{Mitacs Accelerate Intern}{Sept. 2018 - Jan. 2019}{}{
		\item Researched methods to reduce the floating ground effect on wearable electrocardiography sensors to improve performance
		\item Enhanced existing capacitive sensor precision via adaptive filtering using signal injection at the primary reference point 
	}
	\resumeEntry{Alcohol Countermeasures Systems}{Toronto, ON}{Junior Metrology Lab Researcher}{Sept. 2012 - Apr. 2013}{}{
		\item Assisted ongoing R\&D activities developing state of the art electrochemical and optical sensing technologies for breathalyzers
		%\item Collaborated with the Engineering department on product testing, data analysis, and equipment calibration
		\item Authored internal test procedures and developed application specific virtual instruments to automate data acquisition and analysis
	}
	\resumeEntry{Methes Energies International}{Mississauga, ON}{Assistant Chemist}{Sept. 2011 - Apr. 2012}{}{
		\item Performed routine ASTM biochemical analysis employing standardized techniques to ensure accurate results
		\item Monitored performance of industrial biodiesel processors and coordinated process modifications to ensure product conformance
	}
	\resumeEntry{National Research Council Canada}{Victoria, BC}{Co-op Student}{Jan. 2011 - Apr. 2011}{}{
		\item Contributed to the statistical image analysis software (MegaPipe) used to process the Next Generation Virgo Cluster Survey
		\item Performed initial performance evaluations and wrote operating procedures for UBC's Sockeye cloud computing network
		%\item Collaborated in the creation and debugging of the megapipe processing software used for statistical image analysis in the Next Generation Virgo Cluster Survey at the Herzberg Institute of Astrophysics
		%\item Executed the first performance evaluations on the University of Vancouver's new cloud computing network and generated the initial reference documentation and standard operating procedures
	}
	\section{SAMPLE PROJECTS}
	\resumeEntry{MonoPulse Research}{University of Windsor}{Single Ended ECG Measurement Technology}{Sept. 2019 - Apr. 2023}{}{
		\item Performed theoretical and physical evaluations on a variety of measurement methodologies and sensor technologies
		\item Developed a novel single wire ECG acquisition system utilizing transitional capacitive effects and advanced filtering}
	\resumeEntry{Capstone Project}{University of Windsor}{Biometric Identification through ECG Signal}{Sept. 2017 - Oct. 2018}{}{
		\item Created an embedded electronic door unlocking system which performed electrocardiogram based identity verification
		\item Conducted patient assessment with the assistance of the Entrepreneurship Practice and Innovation Centre}
	%Compelling verb + job duty + key skills used = tangible result}
\section{ACTIVITIES \& AFFILIATIONS}
%\resumeSkillEntry{Graduate Assistant}{University of Windsor}{Sept. 2018 - Apr. 2019}
\resumeSkillEntry{IEEE Member}{Toronto Section}{Sept. 2018 - Present}
\resumeSkillEntry{Alumni Representative}{University of Windsor ESF}{November 2018 - Sept. 2021}
\resumeSkillEntry{Volunteer}{Lancer Leadership Conference}{Apr. 2019}
\resumeSkillEntry{Volunteer}{Teaching and Learning Conference}{Feb. 2019}
\resumeSkillEntry{First Robotics Mentor}{Teams 1334 \& 3161}{May 2007 - Sept. 2012}
\section{AWARDS \& HONORS}
%\resumeSkillEntry{GA/TA Award Nomination}{University of Windsor}{May 2019}
\resumeSkillEntry{Fredrick Atkins Graduate Scholarship}{University of Windsor}{May 2019, 2020}
\resumeSkillEntry{Best Capstone Project}{University of Windsor Electrical Engineering Department}{Aug. 2018}
\resumeSkillEntry{Merit Scholarship}{University of Waterloo Electrical Engineering Department}{Sept. 2009}
%\resumeSkillEntry{Engineering Inspiration Award}{First Robotics Waterloo Regional}{Mar. 2009}
%\resumeSkillEntry{RJ Mcarthy}{Halton Catholic District School Board}{June 2009}
\vfill
\end{document}
